Self-calibration of time-domain imaging for exoplanet science, informed by causal structure \\ or \\ A data-driven, pixel-level model to improve the precision of \Kepler\ photometry \\ or \\ Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging

### 2014-08-14 documents/cpm.tex
title, authors, acks

% This file is part of the causal-kepler project
% Copyright 2013 the authors.

@@

\title{%
  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
}
\author{%
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{MPIA},\ref{email}},
  Tom~Barclay\altaffilmark{\ref{Ames}},
  Rob~Fergus\altaffilmark{\ref{Courant}},
  Stefan~Harmeling\altaffilmark{\ref{MPIIS}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}

\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
\altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
  NASA Ames Research Center}
\altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
  Courant Institute of Mathematical Sciences, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
%%   Department of Physics, Oxford University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
%%   Harvard--Smithsonian Center for Astrophysics}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
%%   Department of Physics and Astronomy, University College London}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
%%   McWilliams Center for Cosmology, Carnegie Mellon University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
%%   Department of Astronomy, California Institute of Technology}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
%%   Department of Astronomy, Columbia University}

@@

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Bekki~Dawson (Berkeley),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  David~Schiminovich (Columbia),
  and
  Jake Vanderplas (UW)
for valuable discussions, input, encouragement, and advice.
This project was partially supported by NSF grant IIS-1124794 and NASA grant NNX12AI50G.
This research made use of the NASA Astrophysics Data System.

>>>>

% This file is part of the causal-kepler project
% Copyright 2013, 2014 the authors.

@@

\title{%
  Self-calibration of time-domain imaging for exoplanet science, informed by causal structure%
  \\ or \\
  A data-driven, pixel-level model to improve the precision of \Kepler\ photometry%
  \\ or \\
  Exploiting causal structure to create a data-driven self-calibration of \Kepler\ imaging%
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}},
  others%
}
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Ames}%
%%   NASA Ames Research Center}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Courant}%
%%   Courant Institute of Mathematical Sciences, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Oxford}%
%%   Department of Physics, Oxford University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CfA}%
%%   Harvard--Smithsonian Center for Astrophysics}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{UCL}%
%%   Department of Physics and Astronomy, University College London}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{CMU}%
%%   McWilliams Center for Cosmology, Carnegie Mellon University}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Caltech}%
%%   Department of Astronomy, California Institute of Technology}
%% \altaffiltext{\theaddress}{\stepcounter{address}\label{Columbia}%
%%   Department of Astronomy, Columbia University}

@@

\acknowledgements
It is a pleasure to thank the whole \Kepler\ Team
  for designing, delivering, and operating a great facility,
  and for making all of the data public, in all its rawest forms, through the MAST interface.
We are also pleased to thank
  Ruth~Angus (Oxford),
  Tom~Barclay (Ames),
  Bekki~Dawson (Berkeley),
  Rob~Fergus (NYU),
  Stefan~Harmeling (Dusseldorf),
  Michael~Hirsch (UCL),
  Dustin~Lang (CMU),
  Benjamin~T.~Montet (Caltech),
  David~Schiminovich (Columbia),
  and
  Jake Vanderplas (UW)
for valuable discussions, input, encouragement, and advice.
This project was partially supported by
  NSF grant IIS-1124794,
  NASA grant NNX12AI50G.
  the Moore Foundation,
  and
  the Sloan Foundation.
This research made use of the NASA Astrophysics Data System.
